Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-03-21 02_paper/02_study/paper_methods.Rmd
update method

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR)
```

@@

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

@@

# select relevant columns
quest.data <- quest.data %>% select(LM01_01:LO01_02, LI06_05)

@@

# # define expert and novice with ifelse function
# quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")

>>>>

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm)
```

@@

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% dplyr::select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

@@

# select relevant columns
quest.data <- quest.data %>% dplyr::select(LM01_01:LO01_02, LI06_05)

@@

# define expert and novice with ifelse function
quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")

# creating a matrix
quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

# creating a loop 
# i <- "LM"

for (i in c("LM", "LB", "LP", "LV")) {

loop.data <- quest.data %>% 
  dplyr::select(starts_with(match = i))

quest.table[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 2) ->
quest.table[i, "M"]

# calculating SD
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 2) ->
quest.table[i, "SD"]

# calculating Min
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  min() %>% 
  round(., digits = 2) ->
quest.table[i, "Min"]

# calculating Max
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  max() %>% 
  round(., digits = 2) ->
quest.table[i, "Max"]

# calculating Skewness
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  skewness() %>% 
  round(., digits = 2) ->
quest.table[i, "Skewness"]

# calculating Kurtosis
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  kurtosis() %>% 
  round(., digits = 2) ->
quest.table[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>% 
  cronbach.alpha() 
alpha$alpha

quest.table[i, "alpha"] <- round(alpha$alpha,2)

}

rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
apa_table(
  quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

### 2022-03-21 02_paper/02_study/paper_methods.tex
update method

During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}). The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \ref{fig:teachergazepoint}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57mm (width x depth x height).

@@

@@

@@

>>>>

During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}). The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \ref{fig:teachergazepoint}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

\hypertarget{video-and-audio-recording-equipment}{%
\subsubsection{Video and Audio recording equipment}\label{video-and-audio-recording-equipment}}

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (\url{https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/}) installed in the middle of the lab setting. The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (\url{https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf}) from different angles. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

\hypertarget{questionnaire}{%
\subsubsection{Questionnaire}\label{questionnaire}}

After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior. In addition, participants were asked to give a self-assessment on classroom management by completing the questionnaire after each micro-teaching-unit. The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).

@@

One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

@@

\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M. (2014). Unterrichtsdiagnostik mit EMU. \emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
